---
title: "R Notebook for Yelp Group Assignment Q1"
output: html_notebook

---

```{r}
install.packages("DBI")
install.packages("RMySQL")
library("DBI")
library("RMySQL")

mydb = dbConnect(MySQL(), user='remuser', password='rempwd', dbname='yelp_db', host='ec2-34-216-35-252.us-west-2.compute.amazonaws.com', port=3306)

dbListTables(mydb)
```
```{r}
# Get all the variables mentioned in the hint.
elite_2017= dbGetQuery(mydb, "select distinct user_id from elite_years where year = '2017'")

num_follower = dbGetQuery(mydb, "select friend_id, count(1) from friend group by friend_id")
names(num_follower)[2] = "cnt_followers"

num_follower$is_elite2017 = 0
num_follower$is_elite2017[num_follower$friend_id %in% elite_2017$user_id] = 1

#create the dummy variable if the user is elite in 2016
elite_2016=dbGetQuery(mydb, "select distinct user_id from elite_years where year = '2016'")

num_follower$is_elite2016 = 0
num_follower$is_elite2016[num_follower$friend_id %in% elite_2016$user_id] = 1

#create the variable of times being awarded in history
cnt_elite = dbGetQuery(mydb, "select user_id, count(1) from elite_years where year !='2017' group by user_id")
names(cnt_elite)[2] = "num_elite"

num_follower$num_elite = 0
num_follower$num_elite[num_follower$friend_id %in% cnt_elite$user_id]=cnt_elite$num_elite

#create the variable of number of review of user
cnt_review= dbGetQuery(mydb, "select user_id, count(1) from review group by user_id")
names(cnt_review)[2]='num_review'
num_follower$num_review=0
num_follower$num_review[num_follower$friend_id%in% cnt_review$user_id]=cnt_review$num_review

#create the variable of number of photos of user 
cnt_photo= dbGetQuery(mydb, "select user_id, count(caption) from review as r,photo as p where r.id=p.id group by user_id")
names(cnt_photo)[2] = "num_photo"
num_follower$num_photo=0
num_follower$num_photo[num_follower$friend_id%in% cnt_photo$user_id]=cnt_photo$num_photo

#create the variable of number of tips user gave 
cnt_tip= dbGetQuery(mydb, "select user_id, count(1) from tip group by user_id")
names(cnt_tip)[2] = "num_tip"
num_follower$num_tip=0
num_follower$num_tip[num_follower$friend_id%in% cnt_tip$user_id]=cnt_tip$num_tip
```
Add several variables that might be important in "user" table 
We do think the chracteristics of user can effect its the number of followers.
Hypothesis can be if the user has more funny, it can has more followers.
```{r}
user= dbGetQuery(mydb, "select id, useful, funny, cool, fans, average_stars from user")
```
Merge it to the aggregated table and get the final table
```{r}
names(num_follower)[1] = "user_id"
num_follower=merge(x=num_follower,y=user,by.x='user_id', by.y='id',all.x= TRUE)
num_follower[is.na(num_follower)]= 0
head(num_follower)
```
Do a summary of the variables we are interested that might affect the number of followers
```{r}
summary(num_follower)
```
```{r}
data<-data.frame(num_follower$cnt_followers,num_follower$is_elite2017,num_follower$is_elite2016,num_follower$num_elite,num_follower$num_review,num_follower$num_photo,num_follower$num_tip,num_follower$useful, num_follower$funny, num_follower$cool)

library(dplyr)

cor(data)
```
The boxplot can indicate the relationship between dummy variable and numeric variable.
This boxplot is whether use is elite in 2017 or not against its follower number.
```{r}
boxplot(num_follower$cnt_followers ~ num_follower$is_elite2017, num_follower,ylab = "followers", xlab = "elite2017", ylim = c(0, 150))
```
It looks like there is an obvious difference between elite and non-elite user in the number of followers

Now, let's take time effect into consideration. The boxplot is very similar to the is_elite (2017)
```{r}
boxplot(num_follower$cnt_followers ~ num_follower$is_elite2016, num_follower,ylab = "followers", xlab = "elite2016", ylim = c(0, 150))
```
```{r}
boxplot(num_follower$cnt_followers ~ num_follower$num_elite, num_follower,ylab =" number of follower",xlab =" historical times of elite", ylim = c(0, 1500))
```
We can find the medians is a clear increase as the times of elite increase. 
Also the distances within quarters increase.
```{r}
plot(num_follower$cnt_followers ~ num_follower$num_review,ylab = "followers", xlab = "reviewnumber",col='red',pch=19,bg='green',lwd=4,lty=2)
```
```{r}
boxplot(num_follower$cnt_followers ~ num_follower$num_photo, num_follower,ylab =" Number of follower",xlab ="Photo number ", ylim = c(0, 500))
```
```{r}
plot(num_follower$cnt_followers ~ num_follower$num_tip, ylab = "followers", xlab = "tip number",col='green',pch=19,bg='green',lwd=4,lty=2)
```
```{r}
reg1 = summary(glm(cnt_followers~is_elite2017+is_elite2016+num_elite+num_review+num_photo+num_tip,data=num_follower,family='poisson'))
reg1
```
```{r}
exp(reg1$coefficients) - 1
```
```{r}
reg2 = summary(glm(cnt_followers~is_elite2017+is_elite2016+num_elite+num_review+num_photo+num_tip+useful+funny+cool,data=num_follower,family='poisson'))
reg2
```
```{r}
exp(reg2$coefficients) - 1
```
Through the poisson regression, we can see that the coefficient of is_elite2017 is neagative, which is the opposite of our intuitive belief.
Then we check the correlation table and find that is_elite2017 and is_elite2016 have a high correlation coefficient of 0.814, this multicollinarity may cause some problem.
In this manner, we then built a intersection item of is_elite2017 and is_elite2016.
Meanwhile, since the coefficients of useful, funny and cool are small and their correlationship is high, we may just remove those three variables from the model.
```{r}
num_follower$inter1617=(num_follower$is_elite2017)*(num_follower$is_elite2016)

reg3=summary(glm(cnt_followers~is_elite2017+inter1617+num_elite+num_review+num_photo+num_tip,data=num_follower,family='poisson'))
reg3
```
```{r}
exp(reg3$coefficients) - 1
```
Through this poisson regression, we can see that the variables are all statistically significant. 
When we control the variable of is_elite 2016=0, history elite times, the reviews,photos and tips one posts,it shows that the coefficient of is_elite 2017 is 1.759. Then we compute exp(1.759)-1=4.806. 
It indicates that when controling other variables, if the user is elite in 2017,it will increase 480.6% followers than non-elite in 2017. So yelp elite has higher chance of having more followers.
When we control the variable of is_elite 2016=1, history elite times, the reviews and photos one posts,it shows that the coefficient of is_elite 2017 is 1.759, the coefficient of inter1617 is -0.018. 
Then we compute exp(1.759-0.018)-1=4.703. 
It indicates that when controling other variables, if the user is elite in 2017,it will increase 470.3% followers than non-elite in 2017.
Since whether the user is an elite in 2016 does not necessarily matter, we may just drop the intersection item of inter1617 from our model.
```{r}
reg4=summary(glm(cnt_followers~is_elite2017+num_elite+num_review+num_photo+num_tip,data=num_follower,family='poisson'))
reg4
```
```{r}
exp(reg4$coefficients) - 1
```
Through this poisson regression, we can see that the variables are all statistically significant. 
When we control the variables of history elite times, the reviews, photos and tips one posts, it shows that the coefficient of is_elite 2017 is 1.749. Then we compute exp(1.749)-1=4.745. 
It indicates that when controlling other variables, if the user is elite in 2017,it is associated with an increase of 474.5% followers compared with non-elite in 2017. 
So yelp elites are more likely to have more followers than non-elites.

